Group 1: Tennis 

### 2019-12-07 Group1Prez.Rmd
Update Prez

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

@@

```{r, echo = TRUE}

>>>>

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = FALSE)
source("funs.R")
library(knitr)
library(kableExtra)
library(tidyverse)
set.seed(400)
```

@@

```{r, echo = FALSE}

TDWomen <- as.data.frame(matrix(0, nrow = 4, ncol = 3))

colnames(TDWomen) <- c("P(Win a Rally)", "Empirical P(Win a Game)", "Paper P(Win a Game)" )

TDWomen[1, ] <- c(0.69, 0.71, 0.89)
TDWomen[2, ] <- c(0.63, 0.80, 0.79)
TDWomen[3, ] <- c(0.65, 0.85, 0.83)
TDWomen[4, ] <- c(0.63, 0.77, 0.79)

OurDatWomen <- as.matrix(round(c(pg(TDWomen[1,1]), pg(TDWomen[2,1]), pg(TDWomen[3,1]), pg(TDWomen[4,1])),2))

TDWomen$`Our P(Win a Game)` <-(OurDatWomen)

kable(TDWomen, format = "latex", booktabs = TRUE)%>%
          kable_styling(latex_options = "scale_down")
